Canopy leaf area of a mature evergreen *Eucalyptus* woodland does not respond to elevated atmospheric [CO~2~] but tracks water availability

### 2015-08-18 review1.Rmd
Accounted for (nearly?) all minor comments from reviewer.

l.31 You don’t provide expectation of a seasonal pattern in the abstract, so explaining that there isn’t one is distracting here.
l.37 I would expect that GCB readers would know what FACE stands for, but it might be good to say free air CO2 enrichment to be safe.

**It was already defined both at the top of the Abstract and the second paragraph of the Introduction**

@@

**Changed to LAI throughout the manuscript**

@@

**done**

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

**totally obvious but yeah we'll add that**

@@

**toto. as mentioned above, yes. We have now clarified this.**

@@

**todo. But it happened so why rmeove it.**

@@

@@

**todo. field-verified - clarify**

@@

**no idea what this is all about. Explain that leaf production must equal net increase of LAI (LAIt=2 - LAIt=1) PLUS the litter produced in that time period. It has nothing to do what happened previously. Incomplete litter capture was responded to above**

l.330 methods
l.333 methods

**todo. moved to methods**

@@

**The previous analysis was equivalent to using BA as a covariate, however this is now irrelevant since we have redone the analysis**

@@

**todo. fixed throughout**

@@

@@

@@

**todo. I'd hate to remove this completely - maybe move some of it to introduction to show that the responses sofar are inconclusive so we need more info?**

@@

@@

@@

@@

@@

**todo. Move LAI-BA to the SuppInfo, otherwise keep everything. Six is not a lot.**

>>>>

l.31 You don’t provide expectation of a seasonal pattern in the abstract, so explaining that there isn’t one is distracting here.

l.37 I would expect that GCB readers would know what FACE stands for, but it might be good to say free air CO2 enrichment to be safe.

**It was already defined at the top of the Abstract, when the term EucFACE is introduced.**

@@

**Changed to LAI throughout the manuscript.**

@@

@@

**This sentence is now the topic sentence of the paragraph.**

@@

**Edited the paragraph throughout.**

@@

**Edited the paragraph throughout (and deleted l.79-81).**

@@

**Edited the paragraph throughout, with special attention to tense.**

@@

**FACE was defined in the 2nd paragraph of the definition, here the definition of EucFACE is quite obvious from the statement that the woodland is Eucalyptus-dominated**

@@

**Removed info on precipitation and PET here, as it is explained in more detail in the Methods already.**

@@

**If LAI changes, this must be due to changes in either the production of new foliage, or the lifespan of existing foliage. Both components can be assessed with measurements of litter production in combination with the time dynamics of LAI.** *Expand intro on litter fall a bit!!*

@@

**Added '(unmanaged)'.**

@@

**The estimate of PET is used only here to give an estimate of the ratio P/PET as an indicator of long-term water limitation. The global PET database gives average PET based on 1950-2000 climatology, and is widely used to estimate PET across sites. It is beyond the scope of this manuscript to calculate more accurate estimates of PET, as we do not use PET in any of the subsequent analyses.**

@@

**Removed Ca.**

@@

**Changed the text to 'by multiplying it with an estimate of [...] SLA.**

@@

**The random ring effect accounts for the repeated measures structure of the data; we have now clarified this.**

@@

**We disagree that the outbreak confounded the results; we did not find effects of CO2 on LAI despite the outbreak. Although we did not set out to examine the outbreak, it occurred nonetheless and we think it is informative as the outbreak reflects natural dynamics of Eucalyptus-dominated woodlands. Also, we do not discuss the outbreak in any sort of detail, so removing it from the figure does not shorten the manuscript.**

@@

**We have moved the discussion of discernable effect sizes to the discussion.**

@@

**We verified in the field that no leaf growth was occurring. We have clarified this in this section as well as made reference to Fig. 6, where we have indicated when leaf growth was observed in the field.**

@@

**Moved to methods. We disagree that this method 'assumes litter is grown and lost in the same time period'. Basically, gross leaf production must be equal to the net change in LAI (=the pool of leaves in the canopy) plus the amount of shedded leaf area, as measured by litter production. And to  "this calculation could indicate that a period of reduced Lt and large litter fall was associated with positive leaf production", this is only true if the reduction in LAI is less than the litter produced. In that case the canopy must have produced new leaves in that period to complete the sum of dLAI/dt = leafgrowth - litter. There are no assumptions on when the leaves were produced that show up in the litter traps at that time.**

**We think that the term 'litter production' may be misleading, as the term 'production' seems to indicate that the leaves were 'produced' during that time period, which we certainly do not assume nor imply (in fact, we have shown that leaf lifespan is ca. 1 year).**

l.330 methods

l.333 methods

@@

**The previous analysis was essentially equivalent to using BA as a covariate, however this is now irrelevant since we have redone the analysis.**

@@

**The manuscript was edited throughout to make statements more direct.**

@@

**Removed 'could'.**

@@

**Removed 'very'.**

@@

**It was not the purpose of the manuscript to generalize to other FACE sites, but we feel it is relevant discussion to the results of this study to the other FACE sites. This is informative because the results from the EucFACE do not fit well with a generalization across other FACE sites as presented by Norby and Zak (2011).**

@@

**Deleted sentence on line 381.**

@@

**Here we try to reconcile the apparent inconsistency : we found no effect of CO2 on LAI, but we did find a longer leaf lifespan in elevated CO2. This implies that the fractional allocation to leaves in elevated CO2 has decreased (through mass balance considerations). We have shortened this part of the paragraph.**

@@

**We now define LL in the Methods and use it more consistently throughout.**

@@

**Edited the sentence for clarity.**

@@

**We have moved Fig. 2 to the Supporting Information. We have retained the other figures as we feel they are essential to the manuscript (and six figures does not seem excessive to us).**
